Rule learning for verification from temporal data

### 2016-08-30 Travis/secs/intro.tex
more writing;

Version space learning \cite{lau2000version}.

As a demonstration of the practical use, We plan to implement our algorithm to check for TravisCI configuration errors.
TravisCI is a continous integration tool that allows programmers to automatically run their test suite on every code update.
A recent usage study of TravisCI found that \textasciitilde 15-20\% of failed TravisCI builds are due to "errors" - which means the configuration file was malformed and the software could not even be built\cite{API}.
Using the data from ~\cite{API}, we can also learn that since the start of 2014, approximately 88,000 hours of server time was used on TravisCI projects that resulted in an error status.
This number not only represents lost server time, but also lost developer time, as programmers must wait to verify that their work does not break the build.
If these malformed projects could be quickly statically checked on the client side, both TravisCI and its users could benefit.

>>>>

Version space learning is a machine learning strategy for logical constraint classification\cite{mitchell82}. 
In addition to classification, version spaces have been used for programming-by-example \cite{lau2000version} and error detection \cite{Santolucito2016}.
This approach learns over a set of examples that have been classified into positive and negative examples.
We extend this approach to make use of classified examples with temporal structure, specifically by looking at the differences between sequential examples.

As a concrete use case, we plan to implement our algorithm to check for TravisCI configuration errors.
TravisCI is a continous integration tool that allows programmers to automatically run their test suite on every code update.
A recent usage study of TravisCI found that 15-20\% of failed TravisCI builds are due to "errors" - which means the configuration file was malformed and the software could not even be built \cite{API}.
Using the data from \cite{API}, we can also learn that since the start of 2014, approximately 88,000 hours of server time was used on TravisCI projects that resulted in an error status.
This number not only represents lost server time, but also lost developer time, as programmers must wait to verify that their work does not break the build.
If these malformed projects could be quickly statically checked on the client side, both TravisCI and its users could benefit.
